Towards Transparency and Open Science

### 2023-02-03 manuscript.Rmd
add varios legal matters

\newpage
\clearpage
\thispagestyle{empty}
\null
\clearpage

>>>>

\newpage
\clearpage
\thispagestyle{empty}

# Legal matters

## Digital copy of the work {.unlisted .unnumbered}

This work is made available online under the following source under the terms of the [Creative Commons Universal Public Domain Dedication | CC0](https://creativecommons.org/publicdomain/zero/1.0/):  
<https://aaronpeikert.github.io/thesis/manuscript.pdf>

## Acknowledgement {.unlisted .unnumbered}

During the work on their dissertation, Aaron Peikert was a pre-doctoral fellow of the [International Max Planck Research School on Computational Methods in Psychiatry and Ageing Research (IMPRS COMP2PSYCH)](https://www.mps-ucl-centre.mpg.de/comp2psych) of
the Max Planck Institute for Human Development, Berlin, Germany and University College London, United Kingdom.

## Used resources and aids

I used several digital aids to improve the writing (not the content), including grammerly.com, deepl.com, and mentor.duden.de.
Also, to aid with the clarity of the writing, I asked Andreas Brandmaier, Carli Ochs, Leo Richter, Leonie Haggitte, and Caroline Gahrmann for feedback.
Furthermore, I asked Leo Richter and Maximilian Ernst for help with mathematical notation and typesetting.
I also prompted `ChatGPT` to write a song about reproducibility; while it was amusing, it was not funny enough to make an appearance in the text.

## Declaration of independent work {.unlisted .unnumbered}

I hereby declare that I completed the doctoral thesis independently based on the stated resources and
aids.
I have not applied for a doctoral degree elsewhere and do not have a corresponding doctoral degree.
I have not submitted the doctoral thesis, or parts of it, to another academic institution and the thesis has not been accepted or rejected.
I declare that I have acknowledged the Doctoral Degree Regulations which underlie the procedure of the
Faculty of Life Sciences of Humboldt-Universität zu Berlin, as amended on 5th March 2015.
Furthermore, I declare that no collaboration with commercial doctoral degree supervisors took place, and
that the principles of Humboldt-Universität zu Berlin for ensuring good academic practice were abided by.

\vspace{.5cm}

\hfill{}Aaron Peikert

\newpage
\clearpage
